Collection of BAAD plots

### 2014-06-19 Rmd/baadplotscollection.Rmd
updated plots of pipe model ratios vs. SLA

with(pipe_ba, BARplot(pft,alf_stba, xlab="Plant functional type", 
                          ylab=expression(A[L]/A[W]~base~~(m^2~m^-2)),
                          col=Cols))
with(pipe_ba, BARplot(pft,mlf_stba, xlab="Plant functional type",
                          ylab=expression(M[F]/A[W]~base~~(kg~m^-2)),
                          col=Cols,ymult=1.3
))

par(mfrow=c(1,1))

with(pipe_bh, plot(sla, alf_stbh, pch=19, col=pft, xlim=c(0,50),
                   xlab=expression(Specific~leaf~area~~(m^2~kg^-1)),
                   ylab=expression(A[L]/A[W]~breast~height~~(m^2~m^-2))))
legend("topright", levels(pipe_bh$pft), col=palette(), pch=19)

with(pipe_bh, plot(sla, mlf_stbh, pch=19, col=pft, xlim=c(0,50),
                   xlab=expression(Specific~leaf~area~~(m^2~kg^-1)),
                   ylab=expression(M[F]/A[W]~breast~height~~(m^2~m^-2))))
legend("topright", levels(pipe_bh$pft), col=palette(), pch=19)

@@

  legend("bottomright", as.expression(bquote(Slope==.(slopecomp))),
         bty="n", col="grey", cex=0.7)

  if(legend)legend("topleft", c("Evergreen Angio.","Evergreen Gymno", "Deciduous Angio."), 
                   fill=unlist(pftcols), cex=0.9)  
return(invisible(smfits))
}

>>>>

with(pipe_ba, BARplot(pft,alf_stba, xlab="Plant functional type", 
                          ylab=expression(A[L]/A[W]~base~~(m^2~m^-2)),
                          col=Cols))
with(pipe_ba, BARplot(pft,mlf_stba, xlab="Plant functional type",
                          ylab=expression(M[F]/A[W]~base~~(kg~m^-2)),
                          col=Cols,ymult=1.3
))
```

It seems that *across* PFT's, leaf area to stem cross-sectional area ('area pipe ratio') is more conserved than the leaf mass per unit cross-sectional area ('mass pipe ratio'). Conifers have a much higher leaf mass supported, but end up with similar leaf area.

Within PFT's, the area pipe model ratio is correlated with SLA, but not for the mass pipe ratio.

```{r echo=FALSE, message=FALSE, warning=FALSE}
par(mfrow=c(1,1))
smfit <- sma(alf_stbh ~ sla*pft, log="xy", data=pipe_bh, quiet=TRUE)

plot(smfit,  type='o', pch=19, axes=F,
     xlab=expression(Specific~leaf~area~~(m^2~kg^-1)),
     ylab=expression(A[L]/A[W]~breast~height~~(m^2~m^-2)))
magaxis(side=1:2, unlog=1:2)
legend("topleft", levels(pipe_bh$pft), col=palette(), pch=19)

smfit2 <- sma(mlf_stbh ~ sla*pft, log="xy", data=pipe_bh, quiet=TRUE)
plot(smfit2,  type='p', pch=19, axes=F,
     xlab=expression(Specific~leaf~area~~(m^2~kg^-1)),
     ylab=expression(M[F]/A[W]~breast~height~~(m^2~m^-2)))
magaxis(side=1:2, unlog=1:2)
legend("bottomleft", levels(pipe_bh$pft), col=palette(), pch=19)
```

@@

  legend("bottomright", as.expression(bquote(Slope==.(slopecomp))),
         col="grey", cex=0.7)

  if(legend)legend("topleft", 
                   c("Evergreen Angio.","Evergreen Gymno", "Deciduous Angio."), 
                   fill=unlist(pftcols), cex=0.9,
                   , bg="white", box.col="white", inset=0.01)
return(invisible(smfits))
}
